%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{David Fan} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> 5804 Forest Creek Drive\\ % Address line 1
\> East Amherst, NY 14051 \\ % Address line 2
{\bf GitHub} \> \href{https://github.com/dfan14051}{dfan14051}
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Phone Number} \> (716) 867 1001 \\ % Mobile phone
{\bf Email} \> \href{mailto:david.m.fan@case.edu}{david.m.fan@case.edu} \\ % Email address
{\bf Personal Website} \> http://www.dfan.me
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
    \bf{2015-2019} \> \bf{\href{http://www.case.edu}{Case Western Reserve University} }\\
\>B.S. Computer Science\\
\>B.A. Cognitive Science\\
\>\+
\textit{Cumulative GPA: 3.61}\\
\textit{Computer Science GPA: 3.63}\\
\textit{Cognitive Science GPA: 4.00}
}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{May 2018 -}{Aug 2018}
{Google, }{Sunnyvale, CA}
{Software Engineering Intern}
{
    \begin{itemize-noindent}
        \item{Implemented machine learning driven A/B testing on GSuite's signup page}
        \item{Developed and productionized a system that will effect \textasciitilde10M users}
    \end{itemize-noindent}
}
%------------------------------------------------

\job
{July 2017 -}{Present}
{Case Western Reserve University, }{Cleveland, OH}
{Research Assistant}
{
    \begin{itemize-noindent}
        \item{Assisted Dr. Soumya Ray in multiple-instance learning research}
        \item{Analyzed the performance of the Single-Instance Learning algorithm for multiple-instance learning}
    \end{itemize-noindent}
}
%------------------------------------------------

\job
{May 2017 -}{July 2017}
{Securable.io, }{Cleveland, OH}
{Software Engineering Intern}
{
\begin{itemize-noindent}
\item{Developed a universal OAuth tool to allow for flexible integrations with services that utilize any "OAuth-like" protocol with their APIs}
\item{Implemented integrations into the application's Rails backend with services such as Slack, Google Suite, and Facebook}
\item{Configured and maintained an identity server to allow for integration with enterprise clients' Active Directory servers}
\end{itemize-noindent}
}

\section{Projects}
\project
{Auth Tool}
{General purpose OAuth Ruby gem. Built as an abstraction to the Signet gem allowing for easy API calls to any API protected by an OAuth "based" authentication protocol.}

\project
{Fragmania}
{Final project for Introduction to Computer Game Design. 2D Platformer with a unique radius-based grenade combat mechanic. Written in C\# using the Unity Engine.}

\project
{Matrix RREF Calculator}
{Single-page web app built using vanilla HTML, CSS, and JavaScript. Simplifies matrices into row-reduced echelon form. Made to help with linear algebra homework.}

\section{Activities}
\activity
{April 2017 -}{Feb. 2018}
{HackCWRU}{Director of Logistics}

\activity
{Jan. 2017 -}{Present}
{Association for Computing and Machinery Case Western}{Vice President}
\end{document}
